### 2016-11-23 Chapters/introduction.tex
Add 3 paragraphs in related work about what is modeling for" "

What is modeling?
\textit{Why is it important?
Why so many efforts to model life?
Model are based on 4 principles: question, scope, granularity and mathematical framework (quantitative/qualitative, probabilistic/deterministic, non-linear/linear, dynamic/equilibrium, etc).}

(In each of the following part I point out what is relevant to our question)

>>>>

My recent experience as a teacher taught me that, as of today, a lot of students still choose to study biology in the hope to find a math-free job in science.
They fall from the clouds when you tell them modeling is an important part of a biologist's life.
This misconception usually comes from a bad understanding of what is modeling.
In its general sense, a model depicts and simplifies reality.
Maps, sketches, or pictures satisfy this definition, as do graphs, sets of equations, or even the DNA sequences I store in a text-file on my computer.
Overall, depicting and simplifying reality makes you a modeler, not so much drawing equations on a board.
But this does not change the fact that mathematics are incredible tools for these purpose~\cite{servedio_not_2014,mcgill_calm_2013}.

What makes mathematical modeling so useful in microbial growth studies?
Microbial physiology comes out from the interplay of thousands of chemical reactions that are not necessarily relevant in any given situation.
They usually occur on a short time scale as compared with the organism life span.
They nevertheless have been (and still are) selected by evolutionary processes that occur on long time scales.
These physical limitations strongly impede a full empirical study of growth processes, and it's sometimes hard to test the most simple of our verbal hypothesis.

Since they are designed to abstract away complexity, mathematical models are great tools to deal with such limitations.
Overwhelming number of variables and time scales can be dealt with by choosing the correct framework.
Growth is abstracted into a world of rigor and rules, where logical reasoning can be applied, which allow to test hypothesis~\cite{servedio_not_2014}.
Predictions can be made, "unpacked" into our real world, and confronted with experimental testing~\cite{mcgill_calm_2013}.
Such approach has been successfully applied these decades, creating a diversity a modeling framework which are relevant to growth studies.
